HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
abbreviated

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{\S\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
%\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
\newcommand{\oa}[1]{}
%\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
\newcommand{\bh}[1]{}

@@

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}, or the
annotators are explicitly asked to mark errors, which however suffers from even
lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes metrics
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is HMEANT
\parcite{lo2011structured}.

@@

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by several reasons. 
First, UCCA's set of categories can
be reliably annotated by non-experts after as little as two hours
of training \parcite{marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be stable across translations:
UCCA annotations of translated text usually contain the same set of relations
\parcite{sulem2015conceptual}, indicating that the scheme reflects
a common layer of representation that in a correct translation
is mostly shared between the translation and the source\oa{verb argument structure note?}.

@@

Like HMEANT, HUME defines  a
measure that decomposes over semantic units, rather than strings. 
However, there are important differences in design decisions, which we summarize in this
section.

@@

HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses.
We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.\oa{do we mention here that
  Scenes in their own right correlate less with DA? maybe we should distinguish verbal and non-verbal
  scenes?} Consider the example:

@@

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences) in order to assess the pervasiveness of three phenomena that are not
well supported by HMEANT.
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only consider non-auxiliary instances of ``be''.
Second, nominal argument structures, which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
Third, linkers, that express an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but are again ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
\equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using the NLTK standard tagger. Nominative argument structures are defined as Scenes whose main relation is headed by a noun.}.

@@

\paragraph{One Structure or Two.}
HUME only annotates the source, while HMEANT relies on
two independently constructed structural annotations, one for the reference and one
for the translation.
%First of all, the annotation process is different. We semantically annotate the
%source, then automatically project it to the translation, and ask bilingual
%annotators to assess whether this projection shows a good or bad translation. In
%HMEANT, they semantically annotate both the reference and the translation, then
%align these manually, and assess to what extent they match.
%We see this difference as crucial where semantic analysis is concerned, as it

Not annotating the translation is appealing as it is often impossible to assign a
semantic structure to a low quality translation.
On the other hand, HUME's annotation may be artificially boosting the perceived understandability
of the sentence by allowing access to the source.

>>>>

\newcommand{\com}[1]{}
\newcommand{\secref}[1]{\S\ref{#1}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\XXX}[1]{{\color{red}XXX #1}} % a general todo or comment
%\newcommand{\XXX}[1]{}
\newcommand{\oa}[1]{\footnote{\color{red}OA: #1}}
%\newcommand{\oa}[1]{}
\newcommand{\bh}[1]{\footnote{\color{blue}BH: #1}}
%\newcommand{\bh}[1]{}

@@

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}, or the
annotators are explicitly asked to mark errors, which however suffer from even
lower agreement than ranking \parcite{lommel:etal:mqm-iaa:2014}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes metrics
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is HMEANT
\parcite{lo2011structured}.
%More recent work on MT evaluation proposed measures
%that decompose

@@

% UCCA Motivation
The use of UCCA for semantic MT evaluation measure is motivated by two main reasons. 
First, UCCA's set of categories can
be reliably annotated by non-experts after as little as two hours
of training \parcite{marinotti2014}.
Second, UCCA is cross-linguistically applicable, seeking to
represent what is shared between languages by building on
linguistic typological theory \parcite{Dixon:10a,Dixon:10b,Dixon:12}.
Its cross-linguistic applicability has so far been tested in annotations of
English, French, German and Czech.
%Third, the scheme has been shown to be stable across translations:
%UCCA annotations of translated text usually contain the same set of relations
%\parcite{sulem2015conceptual}, indicating that the scheme reflects
%a common layer of representation that in a correct translation
%is mostly shared between the translation and the source.

@@

We turn to discussing the main differences between HUME and HMEANT,
a semantic measure that measures the translation quality according to its similarity
with a reference, measures in terms of the overlap between their SRL annotations.
%Like HMEANT, HUME defines  a
%measure that decomposes over semantic units, rather than strings. 
%However, there are important differences in design decisions, which we summarize in this
%section.

@@

HMEANT focuses on verbal
argument structures, ignoring other pervasive phenomena such as nominal predicates, inter-clause
relations and copula clauses.
We are not aware of any empirical evaluation that demonstrates that verb argument structure,
taken alone, captures the crux of the sentence semantics meanings.
Moreover, relying only on verbal argument structures is less stable across paraphrases
and translations, as a verbal argument structure
may be translated to a nominal or adjectival argument structure
(e.g., ``after graduation'' may be translated into ``after he graduated'').
This may lead to unjustified penalties low HMEANT score, as the verb
in one structure has nothing to align to in the other.
On the other hand, HUME has been shown to be reasonably stable in an English-French
corpus study \cite{sulem2015conceptual}.

Consider the following example:

@@

There are however a number of other serious consequences on focusing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus (5324 sentences) in order to assess the pervasiveness of three phenomena that are not
well supported by HMEANT.
First, copula clauses are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only consider non-auxiliary instances of ``be''.
Second, nominal argument structures, which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
Third, linkers, that express an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences, but are again ignored by HMEANT.
An example where a linker is omitted in translation in our experiments is
\equo{However, this review\dots}, which was translated to
the German \equo{Diese \"Uberpr\"ufung\dots} (lit. \equo{This review}).
This omission will not be taken into account by HMEANT at all\footnote{Argument structures and linkers are explicitly marked in UCCA. Non-auxiliary instances of ``be'' and nouns are identified using the NLTK standard tagger. Nominal argument structures are here Scenes whose main relation is headed by a noun.}.

@@

\paragraph{One Structure or Two.}
HUME only annotates the source, while HMEANT relies on
two independently constructed structural annotations, one for the reference and one
for the translation.
%First of all, the annotation process is different. We semantically annotate the
%source, then automatically project it to the translation, and ask bilingual
%annotators to assess whether this projection shows a good or bad translation. In
%HMEANT, they semantically annotate both the reference and the translation, then
%align these manually, and assess to what extent they match.
%We see this difference as crucial where semantic analysis is concerned, as it
Not annotating the translation is appealing as it is often impossible to assign a
semantic structure to a low quality translation.
On the other hand, HUME's annotation may be artificially boosting the perceived understandability
of the sentence by allowing access to the source.
